RIScatter: Unifying Backscatter Communication and Reconfigurable Intelligent Surface From a Distribution Perspective

### 2022-11-25 assets/illustration/ambc.tex
:lipstick: Update illustrations

	\node[draw=none] at (0,-1.375) {Legacy\\Transmitter};
	\node[draw=none] at (1,4.375) {Backscatter\\Reader};
	\node[draw=none] at (7,4.375) {Scattering\\Node};
	\node[draw=none] at (8,-1.375) {Legacy\\Receiver};

	\draw[decorate,decoration={waves,segment length=5mm}] (1,-0.5) -- (7.5,-0.5);
	\draw[decorate,decoration={waves,segment length=5mm}] (0.25,1) -- (0.75,3);
	\draw[decorate,decoration={waves,segment length=5mm}] (0.75,0.25) -- (5.5,2.5);
	\draw[decorate,decoration={triangles,segment length=2.5mm}] (5.5,3.5) -- (2.5,3.5);
	\draw[decorate,decoration={triangles,segment length=2.5mm}] (7.5,3) -- (8,1);

	\node[draw=none] at (4,0.35) {Modulated\\Signal};
	\node[draw=none] at (4,3.5) {Superimposed\\Signal};
\end{tikzpicture}

>>>>

	\node[draw=none] at (0,-1.375) {Primary\\Transmitter};
	\node[draw=none] at (1,4.375) {Backscatter\\Reader};
	\node[draw=none] at (7,4.375) {Scatter\\Node};
	\node[draw=none] at (8,-1.375) {Primary\\Receiver};

	\draw[blue,decorate,decoration={waves,segment length=4mm,radius=2mm}] (1,-0.5) -- (7.5,-0.5);
	\draw[lightgray,decorate,decoration={waves,segment length=4mm,radius=2mm}] (0.25,1) -- (0.75,3);
	\draw[lightgray,decorate,decoration={waves,segment length=4mm,radius=2mm}] (0.75,0.25) -- (5.5,2.5);
	\draw[lightgray,decorate,decoration={waves,segment length=4mm,radius=2mm}] (5.5,3.5) -- (2.5,3.5);
	\draw[magenta,decorate,decoration={crosses,segment length=8mm,shape size=1.5mm}] (5.11,3.5) -- (2.5,3.5);
	\draw[lightgray,decorate,decoration={waves,segment length=4mm,radius=2mm}] (7.43,3.28) -- (8,1);
	\draw[lightgray,decorate,decoration={crosses,segment length=8mm,shape size=1.5mm}] (7.525,2.9) -- (8,1);

	\node[draw=none] at (4,0.35) {Modulated};
	\node[draw=none] at (4,3.95) {Doubly-};
	\node[draw=none] at (4,3) {Modulated};
\end{tikzpicture}

### 2022-11-25 assets/illustration/bbc.tex
:lipstick: Update illustrations

	\node[draw=none] at (0,-1.95) {Carrier\\Emitter};
	\node[draw=none] at (5,3.35) {Scattering\\Node};
	\node[draw=none] at (8,-1.95) {Backscatter\\Reader};

	\draw[decorate,decoration={snake,post length=2.5mm},-latex] (1,-1) -- (7.5,-1);
	\draw[decorate,decoration={snake,post length=2.5mm},-latex] (0.5,0) -- (4,2);
	\draw[decorate,decoration={snake,pre length=7.5mm,post length=7.5mm},-latex] (6,2) -- (8,0.35);

>>>>

	\node[draw=none] at (0,-1.95) {Carrier\\Emitter};
	\node[draw=none] at (5,3.35) {Scatter\\Node};
	\node[draw=none] at (8,-1.95) {Backscatter\\Reader};

	\draw[lightgray,decorate,decoration={snake,post length=2.5mm},-latex] (1,-1) -- (7.5,-1);
	\draw[lightgray,decorate,decoration={snake,post length=2.5mm},-latex] (0.5,0) -- (4,2);
	\draw[magenta,decorate,decoration={snake,pre length=7.5mm,post length=7.5mm},-latex] (6,2) -- (8,0.35);

### 2022-11-25 assets/illustration/discrete_outputs.tex
:lipstick: Update illustrations

\begin{tikzpicture}
	\begin{axis}[width=10cm,height=5cm,xmin=0,xmax=6.5,xlabel=$z$,axis x line=middle,axis y line=none,xtick={0,2,3,4,6},xticklabels={$t_0$,$t_1$,$t_2$,$t_3$,$t_4$},xtick style={draw=none},every axis x label/.style={at=(current axis.right of origin),anchor=west},domain=0:6]
		\addplot[mark=*,mark size=0.5pt,only marks,color=gray] {0};
		\addplot[mark=*,mark size=1pt,only marks,color=black] coordinates{(0,0) (2,0) (3,0) (4,0) (6,0)};
		\draw[decorate,decoration={brace,amplitude=10}] (0,0) -- (2,0) node[above,midway,yshift=10]{$\mathcal{R}_1$};
		\draw[decorate,decoration={brace,amplitude=10}] (2,0) -- (3,0) node[above,midway,yshift=10]{$\mathcal{R}_2$};
		\draw[decorate,decoration={brace,amplitude=10}] (3,0) -- (4,0) node[above,midway,yshift=10]{$\mathcal{R}_3$};
		\draw[decorate,decoration={brace,amplitude=10}] (4,0) -- (6,0) node[above,midway,yshift=10]{$\mathcal{R}_4$};
	\end{axis}
\end{tikzpicture}

>>>>

\begin{tikzpicture}
	\begin{axis}[width=10cm,height=5cm,xmin=0,xmax=6.5,ymin=-0.1,ymax=0.1,xlabel=$z$,axis x line=middle,axis y line=none,xtick={0,2,3,4,6},xticklabels={$t_0$,$t_1$,$t_2$,$t_3$,$t_4$},xtick style={draw=none},every axis x label/.style={at=(current axis.right of origin),anchor=west},domain=0:6]
		\addplot[mark=*,mark size=0.5pt,only marks,color=gray] {0};
		\addplot[mark=*,mark size=1pt,only marks,color=black] coordinates{(0,0) (2,0) (3,0) (4,0) (6,0)};
		\draw[decorate,decoration={brace,amplitude=10}] (0,0) -- (2,0) node[above,midway,yshift=10]{$\mathcal{R}_1$};
		\draw[decorate,decoration={brace,amplitude=10}] (2,0) -- (3,0) node[above,midway,yshift=10]{$\mathcal{R}_2$};
		\draw[decorate,decoration={brace,amplitude=10}] (3,0) -- (4,0) node[above,midway,yshift=10]{$\mathcal{R}_3$};
		\draw[decorate,decoration={brace,amplitude=10}] (4,0) -- (6,0) node[above,midway,yshift=10]{$\mathcal{R}_4$};
	\end{axis}
\end{tikzpicture}

### 2022-11-25 assets/illustration/mbc.tex
:lipstick: Update illustrations

	\node[draw=none] at (0,-1.125) {Interrogator};
	\node[draw=none] at (8,4.375) {Scattering\\Node};

	\draw[decorate,decoration={snake,post length=2.5mm},-latex] (0.5,0.75) -- (7,3);
	\draw[decorate,decoration={snake,pre length=2cm,post length=2cm},-latex] (7.25,2.25) -- (0.75,0);

>>>>

	\node[draw=none] at (0,-1.125) {Interrogator};
	\node[draw=none] at (8,4.375) {Scatter\\Node};

	\draw[lightgray,decorate,decoration={snake,post length=2.5mm},-latex] (0.5,0.75) -- (7,3);
	\draw[magenta,decorate,decoration={snake,pre length=2cm,post length=2cm},-latex] (7.25,2.25) -- (0.75,0);

### 2022-11-25 assets/illustration/ris.tex
:lipstick: Update illustrations

	\node[draw=none] at (0,-1) {Transmitter};
	\node[draw=none] at (5,4.4375) {Reflecting\\Element};
	\node[draw=none] at (8,-1) {Receiver};

	\draw[decorate,decoration={waves,segment length=5mm}] (1,-0.25) -- (7.375,-0.25);
	\draw[decorate,decoration={waves,segment length=5mm}] (0.5,0.75) -- (4,3);
	\draw[decorate,decoration={waves,segment length=5mm}] (6,3) -- (8,1.25);

	\node[draw=none] at (4.875,1.125) {Modulated\\Signal};
\end{tikzpicture}

>>>>

	\node[draw=none] at (0,-1) {Transmitter};
	\node[draw=none] at (5,4.4375) {Reflect\\Element};
	\node[draw=none] at (8,-1) {Receiver};

	\draw[blue,decorate,decoration={waves,segment length=4mm,radius=2mm}] (1,-0.25) -- (7.375,-0.25);
	\draw[blue,decorate,decoration={waves,segment length=4mm,radius=2mm}] (0.5,0.75) -- (4,3);
	\draw[blue,decorate,decoration={waves,segment length=4mm,radius=2mm}] (6,3.1625) -- (8,1.25);

	\node[draw=none] at (4.625,1) {Modulated};
\end{tikzpicture}

### 2022-11-25 assets/illustration/riscatter.tex
:bento: Update scattering paradigms
:lipstick: Update illustrations

	\node[draw=none] at (0,-1.25) {Primary\\Transmitter};
	\node[draw=none] at (5,4.5) {RIScatter\\Node};
	\node[draw=none] at (8,-1.25) {Cooperative\\Receiver};

	\draw[decorate,decoration={waves,segment length=5mm}] (1,-0.25) -- (7.375,-0.25);
	\draw[decorate,decoration={waves,segment length=5mm}] (0.5,0.75) -- (4,3);
	\draw[decorate,decoration={triangles,segment length=2.5mm}] (6,3) -- (8,1.25);

	\node[draw=none] at (4,0.875) {Modulated\\Signal};
	\node[draw=none] at (7.8,2.9) {Superimposed\\Signal};
\end{tikzpicture}

>>>>

	\node[draw=none] at (0,-1.25) {Primary\\Transmitter};
	\node[draw=none] at (5,4.5) {RIScatter\\Node};
	\node[draw=none] at (8,-1.25) {Co-located\\Receiver};

	\draw[blue,decorate,decoration={waves,segment length=4mm,radius=2mm}] (1,-0.25) -- (7.375,-0.25);
	\draw[blue,decorate,decoration={waves,segment length=4mm,radius=2mm}] (0.5,0.75) -- (4,3);
	\draw[blue,decorate,decoration={waves,segment length=4mm,radius=2mm}] (6,3.1625) -- (8,1.25);
	\draw[green,decorate,decoration={crosses,segment length=8mm,shape size=1.5mm}] (6.29,2.885) -- (8,1.25);

	\node[draw=none] at (3.5,0.75) {Modulated};
	\node[draw=none] at (8,2.76) {Flexible};
\end{tikzpicture}

### 2022-11-25 assets/illustration/sr.tex
:paintbrush: Update illustrations
:lipstick: Update illustrations

	\node[draw=none] at (0,-1.25) {Primary\\Transmitter};
	\node[draw=none] at (5,4.375) {Scattering\\Node};
	\node[draw=none] at (8,-1.25) {Cooperative\\Receiver};

	\draw[decorate,decoration={waves,segment length=5mm}] (1,-0.25) -- (7.375,-0.25);
	\draw[decorate,decoration={waves,segment length=5mm}] (0.5,0.75) -- (4,3);
	\draw[decorate,decoration={triangles,segment length=2.5mm}] (6,3) -- (8,1.25);

	\node[draw=none] at (4,0.875) {Modulated\\Signal};
	\node[draw=none] at (7.8,2.9) {Superimposed\\Signal};
\end{tikzpicture}

>>>>

	\node[draw=none] at (0,-1.25) {Primary\\Transmitter};
	\node[draw=none] at (5,4.375) {Scatter\\Node};
	\node[draw=none] at (8,-1.25) {Co-located\\Receiver};

	\draw[blue,decorate,decoration={waves,segment length=4mm,radius=2mm}] (1,-0.25) -- (7.375,-0.25);
	\draw[blue,decorate,decoration={waves,segment length=4mm,radius=2mm}] (0.5,0.75) -- (4,3);
	\draw[blue,decorate,decoration={waves,segment length=4mm,radius=2mm}] (6,3.1625) -- (8,1.25);
	\draw[magenta,decorate,decoration={crosses,segment length=20mm,shape size=1.5mm}] (6.29,2.885) -- (8,1.25);

	\node[draw=none] at (3.5,0.75) {Modulated};
	\node[draw=none] at (8,3.15) {Doubly-\\Modulated};
\end{tikzpicture}
